---
title: "Plotting Scottish castles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Scottish castles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = T, message=F, warning=F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ScottishCastles)
library(here)
library(png)
library(showtext)
library(ggplot2)
library(MetBrewer)
library(ggimage)
library(ggpubr)
library(ggspatial)
library(ragg)
```

The first step is to import the different files to create the map. We have 4 disctint files: one polygon shapefile defining the border of Scotland, one klm files where all castles are stored, one excel file containing visited/closed castles and one tiff raster file with the topography of Scotland. Those files have been added to internal data so they can be called directly from the package. The last art is to create a plot with all the different layers 

```{r open files}
data(visits)
data(locations)
data(reg)
data(topo_df)

## ----cleaning dataframes------------------------------------------------------
#clean the 2 dataframes with "clean_names_castles" function
## Put first letter as upper case for all names
# and add "castle" if not in the name
visits_clean <- clean_names_castles(visits)
loc_clean <- clean_names_castles(locations)

#Associate visits, locations and icons
df1=loc_clean
df2=visits_clean

img1= here("Figures","castle_dark_brown.png")
img2= here("Figures","castle_mod_2.png")
img3=here("Figures","castle_orange.png")
img4=here("Figures","castle_mod_2.png")
shapefile<-reg

castles<-merge_castles(df1,df2,img1,img2,img3,img4,shapefile)

# #Get coordinates of castles to place the icons on the map
cast_df<-as.data.frame(as(castles, "Spatial"))


## ----plotting castles, image.width=10, image.height=15,dpi=500----------------
#load background paper
img <- readPNG(here("Figures","Paper.png"))  #fond.png or Paper.png

#Identify different fonts
font_add_google(name = "tangerine", family = "tanguy")
font_add_google(name = "Eagle Lake", family = "tang")
showtext_auto()

#import pictures for the legend
notvis<-readPNG( here("Figures","castle_dark_brown.png"))
vis<-readPNG( here("Figures","castle_mod_2.png"))
clos<-readPNG(here("Figures","castle_orange.png")  )
 
#Plot map
mappy<-ggplot() +
          background_image(img) +
          geom_tile(topo_df,mapping=aes(x=x,y=y,fill=value),show.legend=F) +   #topographic layer
          scale_fill_gradientn(colors=met.brewer("Isfahan1")) +
          geom_sf(data=reg,col="white",show.legend=F,alpha=0.2,size=0.2) +   #coastline layer

          scale_x_continuous(expand=c(0.2,0.3))+
          scale_y_continuous(expand = c(0.3,0.3)) +

          geom_sf(data=castles,mapping=aes(color=Visited),size=0.5) +  #having castle locations as points
           scale_color_manual(name = "Castles",
                              values = c( "Visited" = "black", "Not visited" ="#4F311C",
                                          "Closed" = "#FE9929")) +#castle layer
          annotation_north_arrow(location = "br", which_north = "true",
                                 style = north_arrow_nautical,
                                 pad_x=unit(1,"cm"),pad_y=unit(1.5,"cm"),
                                 height=unit(2,"cm"),width=unit(2,"cm"))+

          geom_image(data=cast_df,aes(x=coords.x1,y=coords.x2,
                                      image=Image_color),size=.023,alpha=0.5) +
          geom_text(mapping = aes(x = 200000, y = 1100000, label = "Castles of Scotland"),
                    family = "tanguy",size=24*.pt,fontface="bold") +

          labs(x="",y="",color="Castles")+

          annotation_raster(vis, xmin =40000, xmax = 55000,
                            ymin =530000, ymax = 560000, interpolate = T) +
          annotation_raster(notvis,  xmin =40000, xmax = 55000,
                            ymin =490000, ymax = 520000, interpolate = T) +
          annotation_raster(clos, xmin =40000, xmax = 55000,
                            ymin = 450000, ymax = 480000, interpolate = T) +

          theme_void() +
          theme(
                    legend.position = c(0.18, 0.1),
                    legend.justification = c("left", "bottom"),
                #    legend.key.size=unit(1, "cm"),
                    legend.spacing.y= unit(0.03, "cm"),
                    legend.spacing.x= unit(0.03, "cm"),
                    legend.text = element_text(family="tang",size=12*.pt),
                    legend.title = element_text(face = "bold",family="tang",size=16*.pt) )

print(mappy)

ggsave(mappy, file=here("Figures","Map_of_Scotland_final.png"),dpi=500,width=10,height=15,units="cm")





```

